%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{etaremune}
\usepackage{hyperref} \usepackage{xcolor}

\name{Matthew T. Luongo} % Your name
\address{(508)~298~9329 \\ mluongo@ucsd.edu} % Your phone number and email
\address{8858 Biological Grade \\ La Jolla, CA 92037} % Your address


\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Scripps Institution of Oceanography}  \hfill {\textit{San Diego, CA}}\\
{\bf University of California, San Diego} \medskip \\
Ph.D., Climate Sciences \hfill {Expected 2025}\\
M.S., Oceanography \hfill {2020}\\
\textit{Advisors}: Professors Shang-Ping Xie \& Ian Eisenman \\
\textit{Committee Members}: Professors Nicholas Lutsko, Jennifer Burney, \& Shantong Sun \medskip

{\bf Harvard University} \hfill{\textit{Cambridge, MA}} \medskip \\
A.B., Earth \& Planetary Sciences, \textit{Magna Cum Laude with Highest Honors}  \hfill {2017} \\ \smallskip
A.B., Engineering Sciences  \\
\textit{Advisor}: Professor Peter Huybers \\ 
\textit{Thesis}: Comparison \& Calibration of Climate Proxy Data in Medieval Europe 
\end{rSection}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Employment}

\textbf{Scripps Institution of Oceanography, UCSD} \hfill {Sep. 2019 - Present} \\ 
Graduate Student Researcher \hfill {San Diego, CA}
\\ \\ 
\textbf{Wildlands Trust} \hfill{Oct. 2018 - Sep. 2019} \\ 
Research Assistant \hfill {Plymouth, MA} 
\\ \\
\textbf{West Monroe Partners} \hfill{Aug. 2017 - Sep. 2018} \\ 
Energy \& Utilities Experienced Consultant \hfill {New York, NY} 
\\ \\ 
\textbf{Harvard University, Dept. of Earth \& Planetary Sciences} \hfill {Apr. 2015 - May 2017}\\ 
Undergraduate Research Assistant \hfill{Cambridge, MA}
%\\ \\ 
%\textbf{Harvard University, Initiative for Science of the Human Past} \hfill {Jun. 2014 - May 2017}\\ 
%Undergraduate Research Assistant \hfill {Cambridge, MA}
%\\ \\ 
%\textbf{Wildlands Trust} \hfill{May 2013 - Jan. 2015} \\ 
%Land Steward \hfill{Plymouth, MA} 

\end{rSection}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Publications}
\textbf{Published}
\begin{etaremune}
\item Tseng, H.-Y., Hwang, Y.-T., Xie, S.-P., Kang, S.M., Tseng, Y.-H., \textbf{Luongo, M.T.}, \& Eisenman, I. (2023). Fast and Slow Responses of the Tropical Pacific to Radiative Forcing in Northern High Latitudes. \textit{Journal of Climate}, \textit{36}(16), pp. 5337-5349. doi:
\textcolor{violet}{\href{https://journals.ametsoc.org/view/journals/clim/36/16/JCLI-D-22-0622.1.xml}{10.1175/JCLI-D-22-0622.1}}
\item \textbf{Luongo, M.T.}, Xie, S.-P., Eisenman, I., Hwang, Y.-T., \& Tseng, H.-Y. (2023). A Pathway for Northern Hemisphere Extratropical Cooling to Elicit a Tropical Response. \textit{Geophysical Research Letters}, \textit{50}, e2022GL100719. doi: \textcolor{violet}{\href{https://agupubs.onlinelibrary.wiley.com/doi/10.1029/2022GL100719}{10.1029/2022GL100719}}
\item Lutsko, N.J., \textbf{Luongo, M.T.}, Wall, C.J., \& Myers, T.A. (2022). Correlation Between Cloud Adjustments and Cloud Feedbacks Responsible for Larger Range of Climate Sensitivities in CMIP6. \textit{Journal of Geophysical Research: Atmospheres}, e2022JD037486. doi: \textcolor{violet}{\href{https://agupubs.onlinelibrary.wiley.com/doi/10.1029/2022JD037486}{10.1029/2022JD037486}}
\item \textbf{Luongo, M.T.}, Xie, S.-P., \& Eisenman, I. (2022). Buoyancy Forcing Dominates the Cross-Equatorial Ocean Heat Transport Response to Northern Hemisphere Extratropical Cooling. \textit{Journal of Climate}, \textit{35}(20), pp. 3071-3090. doi:
\textcolor{violet}{\href{https://journals.ametsoc.org/view/journals/clim/aop/JCLI-D-21-0950.1/JCLI-D-21-0950.1.xml}{10.1175/JCLI-D-21-0950.1}}
\item \textbf{Luongo, M.T.}, Kurbatov, A.V., Erhardt, T., Mayewski, P.A., McCormick, M., More, A.F., Spaulding, N.E., Wheatley, S.D., Yates, M.G., \& Bohleber, P.D. (2017). Possible Icelandic Tephra Found in European Colle Gnifetti Glacier. \textit{Geochemistry, Geophysics, Geosystems}, \textit{18}(11), pp. 3904-3909. doi: \textcolor{violet}{\href{https://agupubs.onlinelibrary.wiley.com/doi/full/10.1002/2017GC007022}{10.1002/2017GC007022}}
\end{etaremune}

%\textbf{Accepted}
%\begin{etaremune}
%\item Tseng, H.-Y., Hwang, Y.-T., Xie, S.-P., Kang, S.M., Tseng, Y.-H., \textbf{Luongo, M.T.}, \& Eisenman, I. Fast and Slow Responses of the Tropical Pacific to Radiative Forcing in Northern High Latitude. Manuscript in press at \textit{Journal of Climate}.
%\end{etaremune}

\textbf{Submitted}
\begin{etaremune}
\item Wan, J.S., Chen, C.-C.-J., Tilmes, S., \textbf{Luongo, M.T.}., Richter, J.H., \& Ricke, K. Unexpected Failure of Regional Marine Cloud Brightening in a Warmer World. Manuscript submitted.
\item \textbf{Luongo, M.T.}, Brizuela, N.G., Eisenman, I., \& Xie, S.-P. Retaining Short-term Variability Reduces Mean State Biases in Wind Stress Overriding Simulations. Manuscript submitted to \textit{Journal of Advances in Modeling Earth Systems (JAMES)}.
\end{etaremune}

%\textbf{In Prep}
%\begin{enumerate}
%\item Peng, Q., Xie, S.-P., Wang, D., \& \textbf{Luongo, M.T.} Indian Ocean Western Boundary Current Changes and Underlying Dynamic Adjustments in a Warming Climate. Manuscript in preparation.
%\item Peng, Q., Xie, S.-P., \textbf{Luongo, M.T.}, Taylor, B.A., \& Geng, Y.F. El Ni\~{n}o-Southern Oscillation Inhibited by Ocean Heating in a Warmer Climate. Manuscript in preparation.
%%\item \textbf{Luongo, M.T.}, Huybers, P.J., McCormick, M., ``Western European heatwave of 1137 C.E. identified in historical texts and paleoclimate reconstructions," in prep for \textit{Earth's Future}.
%\end{enumerate}
\end{rSection}

\begin{rSection}{Presentations}

\textbf{Conference Presentations}
\begin{etaremune}
\item CalGFD, La Jolla, CA, USA (Sep. 2023): \textit{Stress Management Techniques: Overriding Wind Stress in GCMs.} 
\item AGU Fall Meeting, Chicago, IL, USA (Dec. 2022): \textit{Surface and Subsurface Ocean Adjustment and Tropical Pattern Formation Responses to Extratropical Radiative Forcing.} 
\item Scripps Student Symposium, La Jolla, CA, USA (Sep. 2022): \textit{A Surface Pathway by which Northern Hemisphere Extratropical Cooling Elicits a Tropical Response.} 
\item CalGFD, Pasadena, CA, USA (Aug. 2022): \textit{A Surface Pathway by which Northern Hemisphere Extratropical Cooling Elicits a Tropical Response.} 
\item AGU Fall Meeting, New Orleans, LA, USA (Dec. 2021): \textit{The Ocean's Dynamic Response to Northern Hemisphere Cooling and Insights into Cross-Equatorial Energy Transport.} 
\end{etaremune}

\textbf{Conference Posters}
\begin{etaremune}
\item Atlantic Variability and Tropical Basin Interactions Workshop, International Centre for Theoretical Physics, Trieste, Italy (Aug. 2023): \textit{Tropical Subsurface Dynamic Adjustment and Pattern Formation Responses to Idealized Subtropical Low Cloud Forcing}.
\item Graduate Climate Conference, Pack Forest, WA, USA (Oct. 2022): \textit{Coupled Ocean-Atmosphere Processes Lead to La Ni\~{n}a-like Steady-State Response to NH Extratropical Cooling}.
\item Graduate Climate Conference, Virtual (Oct. 2020): \textit{Western European Heatwave Identified in Historical Texts and Paleoclimate Reconstructions.} 
\end{etaremune}

\textbf{Invited Presentations \& Seminars}
\begin{etaremune}
\item Equilibrium Climate Sensitivity \& Cloud Feedback Symposium, Virtual (Aug. 2022): \textit{A Surface Pathway by which Northern Hemisphere Extratropical Cooling Elicits a Tropical Response.}
\item NOAA Climate Sensitivity Task Force Meeting, Virtual (Mar. 2022): \textit{Correlation between Cloud Adjustments and Cloud Feedbacks Responsible for Larger Range of Climate Sensitivities in CMIP6.} 
\end{etaremune}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TEACHING SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Teaching Experience}
\textbf{Guest Lecturer (2023)}: \textit{SIO 173-- Dynamics of the Atmosphere and Climate}, SIO, UCSD. Instructor: Shang-Ping Xie. \\ 
\textbf{2x-Guest Lecturer (2022)}: \textit{SIOC 224-- Numerical Modeling of the Climate System}, SIO, UCSD. Instructor: Ian Eisenman. \\ 
\textbf{Graduate Teaching Assistant (2021)}: \textit{SIO 173-- Dynamics of the Atmosphere and Climate}, SIO, UCSD. Instructors: Shang-Ping Xie \& Ian Eisenman.\\ 
\textbf{Undergraduate Teaching Assistant (2015-2017)}: \textit{PS 11-- Frontiers and Foundations of Modern Chemistry: A Molecular and Global Perspective}, Department of Chemistry, Harvard University. Instructors: Jim Anderson \& Gregg Tucci.

\end{rSection}

%----------------------------------------------------------------------------------------
%	HONORS & AWARDS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Honors \& Awards}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
2023 & Outstanding Student Presentation Award (CalGFD) \\ 
2022-2025 & FINESST Graduate Research Fellowship (NASA) \\ 
2022 & Outstanding Teaching Assistant (SIO) \\ 
2021 & GRFP Honorable Mention (NSF), Outstanding Student Mentor (SIO)  \\
2019-2020 & Regents Fellowship (UCSD) \\ 
2017 & Hoopes Prize for Outstanding Senior Thesis Work (Harvard University) \\
2015 & Undergraduate Summer Research Fellow (Harvard University Center for Environment) \\
2013 &  National Merit Program Commended Scholar, John Joseph Moakley Scholar\\
2012 &  Eagle Scout\\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	MENTORING SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Mentoring and Advising}
\textbf{Research Advising}\\
\hspace*{1cm}Undergraduate researcher: Junyeong Moon (Yonsei University \& UCSD). \\ 
\textbf{Peer Mentoring} \\ 
\hspace*{1cm} Peer Mentor for SIO PhD students Jessica Wan \& Laney Wicker (2020-2022). \\ 
\hspace*{1cm} SIO Peer Mentor Leadership Team (2021-2022). \\

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Leadership and Service}
\textbf{Department} \\ 
\hspace*{1cm}SIO Climate Journal Club: Seminar Organizer (2020-present). \\ 
\hspace*{1cm}SIO Graduate Student Council: Climate Sciences Student Representative (2021-2022). \\ 
\hspace*{1cm}SIO GFD Faculty Search Committee: Student Member (2022). \\ 
\textbf{Field}\\
\hspace*{1cm}CalGFD Organizing Committee (2023). \\ 
\hspace*{1cm}Peer Review: \textit{Journal of Climate}, \textit{Nature Communications}, \textit{Weather \& Climate Dynamics}. \\

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROGRAMMING SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Computer Skills}
\textbf{Substantial Experience:} Matlab, Python, Fortran 77/90, R, ArcGIS \\
\textbf{Additional Experience:} C, HTML, Javascript
\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS & INTERESTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Genera}

\textbf{Memberships:} American Geophysical Union, Sierra Club, Wildlands Trust \\
\textbf{Languages:} English, Latin (8 years) \\
%\textbf{Certifications:} CPR, First Aid, Chainsaw Safety (2014), Subway Track Safety (2018) \\
\textbf{Interests:} Camping, Hiking, Punk Rock, National Parks, Land Conservation, New England Sports, Vinyl Records, Amateur Fermentation \\ 

\end{rSection}

%\begin{rSection}{Housing References}
%
%\textbf{Michele Kabbai:} \\
%Current Landlord: 8310 Regents Rd, Unit 3F, San Diego, CA 92122 \\  
%kabbai.ramesh@gmail.com \\ 
%619-890-9298 \\ 
%
%\textbf{Alan Zelkowitz:} \\ 
%Former Landlord: 764a Franklin Ave, Unit 4, Brooklyn, NY 11238 \\ 
%alanz2003@aol.com \\ 
%917-655-9078 \\ 
%
%\end{rSection}




%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
